### 2014-05-07 sprout_eval.tex
Import Remy
Revise through some of eval
Put tables in figures

\section{Evaluation}
\label{s:eval}

@@

Although it is purely end-to-end, Sprout's delays are even lower than
Cubic-over-CoDel. However, this comes at a cost to
throughput. (Figures are given in the table in the introduction.)
Sprout-EWMA achieves within 6\% of the same delay as Cubic-over-CoDel,
with 30\% more throughput.

@@

\footnotesize
\def\svgwidth{\columnwidth}\input{codelcomp.pdf_tex}

>>>>

\section{Evaluation}
\label{sprout:eval}

@@

Although it is purely end-to-end, Sprout's delays are even lower than
Cubic-over-CoDel. However, this comes at a cost to
throughput. (Numerical results are given in Figure~\ref{f:sproutvsaqm}.)
Sprout-EWMA achieves within 6\% of the same delay as Cubic-over-CoDel,
with 30\% more throughput.

@@

%\footnotesize
\def\svgwidth{\columnwidth}\input{codelcomp.pdf_tex}

### 2014-05-07 sprout_intro.tex
Put tables in figures

\begin{figure}
\caption{Skype and Sprout on the Verizon LTE downlink trace. For Skype, overshoots in throughput lead to large standing queues. Sprout tries to keep each
packet's delay less than 100~ms with 95\% probability.}
\label{fig:skypevssprout}
\vspace{\baselineskip}
\footnotesize\def\svgwidth{\columnwidth}\input{newfigure1.pdf_tex}
\end{figure}

@@

The following table summarizes the average relative throughput
improvement and reduction in self-inflicted queueing
delay\footnote{This metric expresses a lower bound on the amount of
  time necessary between a sender's input and receiver's output, so
  that the receiver can reconstruct more than 95\% of the input
  signal. We define the metric more precisely in \S\ref{sprout:eval}.} for
Sprout compared with the various other schemes, averaged over all four
cellular networks in both directions. Metrics where Sprout did not
outperform the existing algorithm are highlighted in red:

\vspace{\baselineskip}

\begin{centering}
\noindent \begin{tabular}{|l|c|c|}
\hline
App/protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.32~s) \\
\hline
Skype & $2.2\times$ & $7.9\times$ (2.52~s) \\
Hangout & $4.4\times$ & $7.2\times$ (2.28~s) \\
Facetime & $1.9\times$ & $8.7\times$ (2.75~s) \\
\hline
Compound & $1.3\times$ & $4.8\times$ (1.53~s) \\
TCP Vegas & $1.1\times$ & $2.1\times$ (0.67~s) \\
LEDBAT & $1.0\times$ & $2.8\times$ (0.89~s) \\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$ (25~s)\\
\hline
Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}

\end{centering}

\vspace{\baselineskip}

@@

Sprout and Sprout-EWMA represents different tradeoffs in their
preference for throughput versus delay.  As expected, Sprout-EWMA
achieved greater throughput, but also greater delay, than Sprout. It
outperformed TCP Cubic on both throughput and delay. Despite being
end-to-end, Sprout-EWMA outperformed Cubic-over-CoDel on throughput
and approached it on delay:

\vspace{\baselineskip}
\begin{centering}
\noindent \begin{tabular}{|l|c|c|}
\hline
Protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout-EWMA} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout-EWMA & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.53~s) \\
\hline
Sprout & $2.0\times$ & \cellcolor{red!20}$0.60\times$ (0.32~s) \\
Cubic & $1.8\times$ & $48 \times$ (25~s)\\
\hline
Cubic-CoDel & 1.3 $\times$ & \cellcolor{red!20}$0.95\times$ (0.50~s)\\
\hline
\end{tabular}

\end{centering}

\vspace{\baselineskip}

>>>>

\begin{figure}
\caption{Skype and Sprout on the Verizon LTE downlink trace. For Skype, overshoots in throughput lead to large standing queues. Sprout tries to keep each
packet's delay less than 100~ms with 95\% probability.}
\label{fig:skypevssprout}
\vspace{\baselineskip}
\def\svgwidth{\columnwidth}\input{newfigure1.pdf_tex}
\end{figure}

@@

Figure~\ref{f:sproutcompe2e} summarizes the average relative throughput
improvement and reduction in self-inflicted queueing
delay\footnote{This metric expresses a lower bound on the amount of
  time necessary between a sender's input and receiver's output, so
  that the receiver can reconstruct more than 95\% of the input
  signal. We define the metric more precisely in \S\ref{sprout:eval}.} for
Sprout compared with the various other schemes, averaged over all four
cellular networks in both directions.

\begin{figure}
\caption{Sprout compared with other end-to-end schemes. Metrics where
  Sprout did not outperform the existing algorithm are highlighted in
  red.}
\label{f:sproutcompe2e}

\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
App/protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.32~s) \\
\hline
Skype & $2.2\times$ & $7.9\times$ (2.52~s) \\
Hangout & $4.4\times$ & $7.2\times$ (2.28~s) \\
Facetime & $1.9\times$ & $8.7\times$ (2.75~s) \\
\hline
Compound & $1.3\times$ & $4.8\times$ (1.53~s) \\
TCP Vegas & $1.1\times$ & $2.1\times$ (0.67~s) \\
LEDBAT & $1.0\times$ & $2.8\times$ (0.89~s) \\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$ (25~s)\\
\hline
Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}
\end{center}

\end{figure}

@@

Sprout and Sprout-EWMA represents different tradeoffs in their
preference for throughput versus delay.  As expected, Sprout-EWMA
achieved greater throughput, but also greater delay, than Sprout. It
outperformed TCP Cubic on both throughput and delay. Despite being
end-to-end, Sprout-EWMA outperformed Cubic-over-CoDel on throughput
and approached it on delay (Figure~\ref{f:sproutvsaqm}).

\begin{figure}
\caption{Sprout and Sprout-EWMA achieve comparable results to Cubic
  assisted by in-network active queue management.}
\label{f:sproutvsaqm}

\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
Protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout-EWMA} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout-EWMA & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.53~s) \\
\hline
Sprout & $2.0\times$ & \cellcolor{red!20}$0.60\times$ (0.32~s) \\
Cubic & $1.8\times$ & $48 \times$ (25~s)\\
\hline
Cubic-CoDel & 1.3 $\times$ & \cellcolor{red!20}$0.95\times$ (0.50~s)\\
\hline
\end{tabular}

\end{center}

\end{figure}
